|

### 2025-01-10 output/seminar-slideshow.qmd
Update items color palette to plot up to 5 items

::::: column
::: fragment
$$
  cos \, \mathbf{\alpha}_i = \frac{\mathbf{a}_i}{\sqrt{\mathbf{a}_i^T\mathbf{a}_i}}
$$
:::

@@

ITEMS_PALETTE <- c(
  PALETTE_BLUE["normal"],
  PALETTE_RASPBERRY["normal"],
  PALETTE_APPLE["normal"]
) |>
  unname() |>
  setNames(paste(1:3, sep = '_'))

@@

@@

::: fragment
$$
  cos \, \mathbf{\alpha}_i = \frac{\mathbf{a}_i}{MDISC_i}
$$
:::

>>>>

::::: column
::: fragment
$$
  \cos \, \mathbf{\alpha}_i = \frac{\mathbf{a}_i}{\sqrt{\mathbf{a}_i^T\mathbf{a}_i}}
$$
:::

@@

ITEMS_PALETTE <- c(
  PALETTE_BLUE["normal"],
  PALETTE_RASPBERRY["normal"],
  PALETTE_APPLE["normal"],
  PALETTE_TANGERINE["normal"],
  PALETTE_UNED["normal"]
) |>
  unname() |>
  setNames(1:5)

@@

## Propiedades: $\cos \, \mathbf{\alpha}$ {.smaller}

::: notes
:::

@@

::: fragment
$$
  \cos \, \mathbf{\alpha}_i = \frac{\mathbf{a}_i}{MDISC_i}
$$
:::
